---
title: "Assignment1"
author: "Team2"
date: "2021/1/31"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(dplyr) 
library(rcompanion) 
library(readxl) 
library(tidyr) 
library(ggplot2) 
library(car)
```

```{r}
PO2 <- read_excel("Purchase Orders 2.xlsx")
head(PO2)
```

Q2a
```{r}
PO30 = PO2 %>% rename("v2"="A/P Terms (Months)","v1"="Cost per order") %>% filter(v2==30)

a90u = mean(PO30$v1) - 
    qt(0.05, df=nrow(PO30)-1)  * sd(PO30$v1)/sqrt(nrow(PO30)) 
a90l = mean(PO30$v1) + 
    qt(0.05, df=nrow(PO30)-1)  * sd(PO30$v1)/sqrt(nrow(PO30))  
print(cbind(a90l,a90u ), digits=4) 
```
```{r}
POa2 = PO2 %>% rename("v3"="Arrival Time")
POa22= PO2 %>% rename("v3"="Arrival Time") %>% filter(v3<6)
a2p = nrow(POa22)/nrow(POa2)

a95u <- a2p + (qnorm(0.025) * sqrt(a2p*(1-a2p)/nrow(POa2)))
a95l <- a2p - (qnorm(0.025) * sqrt(a2p*(1-a2p)/nrow(POa2)))
print(cbind(a95l, a95u),digits=3)
```
The first interval means that we have 90% confidence(Probability) that the mean of [Cost per order] for orders with A/P Terms of 30 months are in the range of 22367 to 34841. The estimate is for the sample.
The second interval means that we have 95% confidence(Probability) that the proportion of orders with [Arrival Time] less than 6 days is in the range of 0.355 to 0.177. The estimate is for the population.


Q2b
1) One-side test
h0:P>0.15
h1:p<=0.15
```{r}
POa2 = PO2 %>% rename("v3"="Arrival Time")
POa22= PO2 %>% rename("v3"="Arrival Time") %>% filter(v3<6)
a2p = nrow(POa22)/nrow(POa2)
z = (a2p - 0.15) / sqrt(0.15*(1-0.15)/nrow(POa2))
cv95 = qnorm(0.05)
z
cv95
z<cv95
```
We fail to reject the null hypothesis, so it's true that the proportion is greater than 15%.

2)Two-side test
h0:mean1=mean2
h1:mean1!=mean2
```{r}
PO31<- PO2 %>% rename("v2"="A/P Terms (Months)","v3"="Arrival Time") %>% filter(v2==30)
PO32<- PO2 %>% rename("v2"="A/P Terms (Months)","v3"="Arrival Time") %>% filter(v2!=30)

t.test(PO31$v3,PO32$v3)

```
p is large so we accept the h0 that mean1=mean2

3) Anova Assumptions Tests
Normality Test
```{r}
PO<- PO2 %>% rename("v2"="Arrival Time","v3"="Supplier") 
PO$Group <- 4

PO$Group[PO$v3 %in% c("Fast-Tie Aerospace","Hulkey Fasteners")] <- "1"
PO$Group[PO$v3 %in% c("Alum Sheeting","Durrable Products","Manley Valve")] <- "2"
PO$Group[PO$v3 %in% c("Steelpin Inc.","Spacetime Technologies","Pylon Accessories")] <- "3"

g1 <-PO %>% filter(Group=="1") 
g2 <-PO %>% filter(Group=="2") 
g3 <-PO %>% filter(Group=="3") 
hist(g1$v2, main="Histogram for `Group1`", xlab="Arrival Time")
hist(g2$v2, main="Histogram for `Group2`", xlab="Arrival Time")
hist(g3$v2, main="Histogram for `Group3`", xlab="Arrival Time")
```
Normality Test
```{r}
par(mfcol=c(1,3))
qqnorm(g1$v2, main="QQplot for `Group1`", xlab="Arrival Time")
qqline(g1$v2)
qqnorm(g2$v2, main="QQplot for `Group2`", xlab="Arrival Time")
qqline(g2$v2)
qqnorm(g3$v2, main="QQplot for `Group3`", xlab="Arrival Time")
qqline(g3$v2)
```
Normality Test
```{r}
par(mfcol= c(1,1))
boxplot(PO$v2 ~ PO$Group)
```
Normality Test
```{r}
lapply(list(g1,g2,g3), 
       function(sa) 
         {
         shapiro.test(sa$v2)
         }) # applying test on each vector in list
```
```{r}
table(PO$Group)
```
Equal Variance
```{r}
fligner.test(v2~Group,PO)
```
```{r}
leveneTest(v2~ as.factor(Group), PO)
```
Run One-Way Anova
```{r}
aov.amt <- aov(PO$v2 ~ as.factor(PO$Group)) 
summary(aov.amt)
```
H0:Mean arrival time for 3 groups are the same
H1:Mean arrival time for at least one group is different from the others
Since p is rather small we reject the h0, so we conclude that the arrival time for at least one group is different from other groups.


