---
title: 'Homework Assignment 2'
subtitle: "IS5126 Hands-on with Applied Analytics"
author: "Team2"
date: 'Due by: Feb 21st, 2021 5:00 PM'
output: 
  pdf_document:
    df_print: kable
    highlight: tango
    fig_width: 6
    fig_height: 4
    fig_caption: true
linkcolor: MidnightBlue
header-includes:
- \usepackage{xcolor}
---
    
## Preparation

```{r load-libraries, echo=TRUE, message=FALSE, warning=FALSE}
# load required packages
library(dplyr)
library(wooldridge)
library(rcompanion)
library(readxl)
library(tidyr)
library(ggplot2) 
library(car)

```

## Homework 2 Part B: Assignment Submission

### Question 2  (20 Marks)

- Dataset required: `data('recid')`

Recidivism rate in Singapore is 24% in 2016 (https://data.gov.sg/dataset/recidivism-rate). Criminals tend to replapse into criminal offense after the release from the prison. `recid.csv` contains 1445 observations of recidivism cases in United States. 

```{r q3-data-input, echo=TRUE}
recid = read.csv(file = 'recid.csv', header= TRUE)
```


(2a) Based on previous experience, prison staffs suggest that the recidivism period `durat` (duration between release and follow-up offense) is affected by prison serving time `tserved`, previous drug use `drugs`, achcohol abuse `achcohol` and number of prior convictions `priors`. They currently consider if they should retain the prison working program to improve the situation of follow-up offense after prison release. Run a multivariate linear regression: `durat ~ tserved + drugs + alcohol + priors + workprg`. Interpret the meaning of coefficients before `tserved` and `workprg` and discuss if prison working program should be retained from your regression result. (6 points)

\textcolor{BrickRed}{**Type your answer here**}

```{r q2a, echo=TRUE}
# your code here

fit1a = lm(durat ~ tserved + drugs + alcohol + priors + workprg,recid) 
summary(fit1a) 
## Analysis of Variance in Linear Regression (ANOVA)
# generate ANOVA table after fitting 
anova1a = aov(fit1a)
print(summary(anova1a))
#anova p-value: < 2.2e-16, reject h0 that all groups have the same mean
#Running Residual Diagnostics

plot(fit1a, which = c(1,2), caption = list("Resid vs. Fitted", "Normal Q-Q"))

#Scaled
#fit1a1 = lm(scale(durat) ~ scale(tserved) + scale(drugs) + scale(alcohol) + scale(priors) + scale(workprg), recid)
#summary(fit1a1)


```
Coefficients before tserved: On average a one-unit increase in prison serving time results in 0.25630 decrease in duration between release and follow-up offense.
Coefficients before workprg: On average a one-unit increase in prison working program results in 2.32777  increase in duration between release and follow-up offense.
Because the p value of coefficient workprg is 0.105816 > 0.05, it shows little contribution to the duration between release and follow-up offense. Consider the financial consumption the program cost, the program should not be retained.


(2b) The warden of prison decided to terminate the working program. Do you agree with his/her decision? Why or why not? (6 points)

Hint: One of most effective way to be critical is to check the assumptions used to reach the conclusion and decision.

\textcolor{BrickRed}{**Type your answer here**}
```{r}
#Anova test
anova_w = aov(fit1a)
print(summary(anova_w))
```
From the anova test we know that coefficient tserved, alcohol, priors are effective, so the first assumption of the linear regression is satisfied. We have checked assumption "Biased Error".
Then we will check assumption "Heteroskedasticity".

```{r q2b, echo=TRUE}
# your code here

plot(fit1a, which = c(1,2), caption = list("Resid vs. Fitted", "Normal Q-Q"))
# conduct a Breusch-Pagen (BP) test for heteroskedasticity
library(lmtest)
bptest(fit1a)
est = summary(fit1a)
est.robust = coeftest(fit1a, vcov = sandwich)
# make a comparison between s.e. and robust s.e.
# let's list the coef and two different versions of s.e.'s
coef.table.compare = cbind(est$coefficients[,1:2], est.robust[,1:2]) %>% round(4)
colnames(coef.table.compare) = c("Duration.","SE_OLS", "Duration_White", "SE_White")
print(coef.table.compare)
```
The BP test has a p value small enough to reject the h0 of homoskedasticity.
That's why we use robust standard error. 
For assumption normality, we have addressed it with large samples.
In conclusion, our linear regression model satisfy the assumptions with robust standard error and we determined the prison working program as a variable with little contribution and should be terminated. We agree with the warden.


(2c) Criminal offense lawyers usually fight for supervised release of the offender. Given five vairables in `recid` data set: `super`, `rules`, `age`, `tserved`, and `married`, how could you help the law firm to predict the outcome of a recent case given that a 32-year old married client has been serving the jail time for 3 years and 7 months and during which broken no rule in the prison? Choose a proper model with those 5 variables and interpert meaning of the coefficients in your model. (8 point)

Note: Classify a successful supervised release case if probability of supervised release is greater or equal to 0.5; and no supervised release otherwise.


\textcolor{BrickRed}{**Type your answer here**}

```{r q2c, echo=TRUE}
# your code here
fit1c=glm(super~ rules + age + tserved + married,family=binomial,data=recid,control=list(maxit=50))
summary(fit1c)
exp(cbind(OddsRatio = coef(fit1c), confint(fit1c)))
```
Consider the supervised binomial label is our goal, we choose logistic regression model.
The p value of the coefficients is small enough to demonstrate their effectiveness, and the logistic model is strong.
Coefficient Interpretation:
Every one unit increase of rules violation counts results in the log-odds of Pr(release supervised) decrease by 0.2457807.
Every one unit increase of age results in the log-odds of Pr(release supervised) decrease by 0.0018723.
Every one unit increase of time served in the prison results in the log-odds of Pr(release supervised) increase by 0.0324274.
Every one unit increase of married results in the log-odds of Pr(release supervised) increase by 0.5080370.

Then we predict the case using prediction interval.
```{r}
ndata=data.frame(rules=0,age=384,tserved=43,married=1)
pre1=predict(fit1c,newdata=ndata,interval="prediction")
#it's the logit
p=exp(pre1)/(1+exp(pre1))
print(p)
```
So we predict this case has a 0.9051092 probability of being supervised release, and classify it as a successful supervised release.


